### 2013-06-24 trunk/network-science/paper.tex

\begin{abstract}
We address the dynamic properties of typical social networks, in which people
are considered as vertices while relations are considered as edges. We suppose
the evolution of a social network overtime includes new
connections between existing or newly created nodes, and also assume the graph
will evolve as a typical social network. We study the activity and centrality
metrics for nodes in such graphs by regulating a series of reasonable
properties the metrics should satisfy. We then formally define our metrics and
give their mathematical analysis. We have developed a practical based framework
to maintain the evolving large-scale network and the algorithm to compute our
metrics including historical queries in preferable time and space consumption.
Finally, we use a simple model to generate evolving data from existing social
network data and compare our metrics to static metrics. The results could imply
that dynamic centrality is more capable in spotting hot social events.\\[1.5em]

\noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
centrality, online algorithm.
\end{abstract}
% \tableofcontents
\newpage

>>>>

\begin{abstract}
We address the dynamic properties of typical social networks. We suppose
the evolution over time only includes new connections between existing or newly
created nodes. We study the activity and centrality
metrics for nodes in such graphs by regulating a series of reasonable
properties the metrics should satisfy. We then formally define our metrics and
give their mathematical analysis. We have developed a practice based framework
to maintain the evolving large-scale network and the algorithm to compute our
metrics including historical queries in preferable time and space consumption.
Finally, we use a simple model to generate evolving data from existing social
network data and compare our metrics to static metrics. The results could imply
that dynamic centrality is more capable in spotting hot social events.

\smallskip
\noindent \textbf{Keywords:} social network, dynamic graph, vertex activity,
centrality, online algorithm.
\end{abstract}
% \tableofcontents
\newpage
